---
title: "500 Analyse Biodiv-RS"
output: html_notebook
---

```{r, include = FALSE}
source("C:/Users/tnauss/permanent/plygrnd/KI-Hyperspec/HySpec_KiLi/src/000_set_environment.R")

dir.create(path_analysis_sr, showWarnings = FALSE)

all_models = readRDS(file.path(path_compile_analysis_sr, "models_sr.rds"))


# Collect model performance
gam_sr = modelPerformance(all_models[["gam"]])
pls_sr = modelPerformance(all_models[["pls"]])
rf_sr = modelPerformance(all_models[["rf"]])

summary(gam_sr)
summary(pls_sr)
summary(rf_sr)

# Get trophic levels
tl = read.table(file.path(path_meta, "trophic_levels.csv"), header = TRUE, sep = ";")
gam_sr = merge(gam_sr, tl, by.x = "resp", by.y = "Species")
pls_sr = merge(pls_sr, tl, by.x = "resp", by.y = "Species")
rf_sr = merge(rf_sr, tl, by.x = "resp", by.y = "Species")

# Arrange levels and species names
pls_sr$Level = factor(pls_sr$Level, levels(pls_sr$Level)[c(1, 5, 4, 3, 6, 2)] )
pls_sr$resp = as.character(pls_sr$resp)
pls_sr$resp = substr(pls_sr$resp, 3, nchar(pls_sr$resp))
pls_sr$resp = gsub("(^[[:alpha:]])", "\\U\\1", pls_sr$resp, perl=TRUE)
pls_sr$resp = factor(pls_sr$resp, unique(pls_sr$resp[order(pls_sr$Level, pls_sr$resp)]))


rf_sr$Level = factor(rf_sr$Level, levels(rf_sr$Level)[c(1, 5, 4, 3, 6, 2)] )
rf_sr$resp = as.character(rf_sr$resp)
rf_sr$resp = substr(rf_sr$resp, 3, nchar(rf_sr$resp))
rf_sr$resp = gsub("(^[[:alpha:]])", "\\U\\1", rf_sr$resp, perl=TRUE)
rf_sr$resp = factor(rf_sr$resp, unique(rf_sr$resp[order(rf_sr$Level, rf_sr$resp)]))
```

# Compare PLS and RF
```{r, echo=FALSE}
models_sr = rbind(pls_sr[, -4], rf_sr[, -4])
models_sr$mptype = paste0(models_sr$mtype, "_", models_sr$ptype)
models_sr$mptype = factor(models_sr$mptype, levels = c("pls_elsp", "rf_elsp",
                                                       "pls_elui", "rf_elui",
                                                       "pls_kmra", "rf_kmra",
                                                       "pls_spec", "rf_spec"))

ggplot(data = models_sr[models_sr$mtype == "pls" & 
                          (models_sr$ptype == "elui" | models_sr$ptype == "spec"),], 
       aes(x = resp, y = RMSE_normSD, fill = mptype)) + 
  geom_boxplot() +
  geom_hline(yintercept=c(0.5,1), linetype="dashed", color = "black") + 
  scale_fill_brewer(palette="Dark2") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(list(x = "Species groups", y = "RMSEn", fill = "Model set"))



ggplot(data = models_sr[models_sr$mtype == "rf" & 
                          (models_sr$ptype == "elui" | models_sr$ptype == "spec"),], 
       aes(x = resp, y = RMSE_normSD, fill = mptype)) + 
  geom_boxplot() +
  geom_hline(yintercept=c(0.5,1), linetype="dashed", color = "black") + 
  scale_fill_brewer(palette="Dark2") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(list(x = "Species groups", y = "RMSEn", fill = "Model set"))


ggplot(data = models_sr[models_sr$mtype == "rf" & models_sr$ptype == "spec",], 
       aes(x = resp, y = RMSE_normSD, fill = Level)) + 
  geom_boxplot() +
  geom_hline(yintercept=c(0.5,1), linetype="dashed", color = "black") + 
  scale_fill_brewer(palette="Dark2") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  labs(list(x = "Species richness", y = "RMSEn", fill = "Trophic level"))
```

```{r, echo=FALSE}
pls_rf_sr = merge(pls_sr, rf_sr, by = c("ptype", "resp", "Resample"), all.y = TRUE)
colnames(pls_rf_sr)[grep("\\.x", colnames(pls_rf_sr))] = 
  gsub("\\.x", "_pls", colnames(pls_rf_sr)[grep("\\.x", colnames(pls_rf_sr))])
colnames(pls_rf_sr)[grep("\\.y", colnames(pls_rf_sr))] = 
  gsub("\\.y", "_rf", colnames(pls_rf_sr)[grep("\\.y", colnames(pls_rf_sr))])
# nrow(pls_rf_sr)

ptypes = c("elui", "kmra", "spec", "elsp")
perf_check = lapply(ptypes, function(pt){
  subdf = pls_rf_sr[!is.na(pls_rf_sr$RMSE_pls) & 
                      pls_rf_sr$ptype == pt &
                      pls_rf_sr$Resample == "Mean", ]
  rownames(subdf[subdf$RMSE_pls < subdf$RMSE_rf, ])
})
names(perf_check) = ptypes
```

# Check performance of PLS and RF
```{r, echo = FALSE}
for(i in seq(length(perf_check))){
  rmse_perf = sort(round(1-pls_rf_sr[as.numeric(perf_check[[i]]), "RMSE_pls"] / 
                           pls_rf_sr[as.numeric(perf_check[[i]]), "RMSE_rf"],2))
  var_rf_prct = sort(round(pls_rf_sr[as.numeric(perf_check[[i]]), "nvars_rf"] / 
                             pls_rf_sr[as.numeric(perf_check[[i]]), "nvars_pls"],2))
  level_pls = sort(table(pls_rf_sr[as.numeric(perf_check[[i]]), "Level_pls"]))
  print(names(perf_check[i]))
  print(pls_rf_sr[as.numeric(perf_check[[i]]),])
  cat("RMSE (1 - PLS/RF):", rmse_perf, "\n")
  cat("Var number (RF/PLS):", var_rf_prct, "\n")
  cat("Levels with PLS is better:", level_pls, "\n")
  cat("\n\n")
}
```

# Collect variable importance
## Number of variables
```{r}
pls_rf_sr_long = melt(pls_rf_sr[pls_rf_sr$Resample == "Mean", c(1, 2, 6, 13)], id.vars = c("ptype", "resp"))
ggplot(data = pls_rf_sr_long, aes(x = variable, y = value, fill = ptype)) +
  geom_boxplot() + 
  labs(list(x = "Models", y = "Number of variables" ,
            fill = "Predictor Set")) +
  theme_bw()
```


# Variable importance for PLS
```{r, echo=FALSE}
var_imp <- compVarImp(all_models[["pls"]][["spec"]]@model[[1]], scale = FALSE)
# plotVarImp(var_imp)
plotVarImpHeatmap(var_imp, xlab = "Species", ylab = "Band")
```

# Variable importance for RF
```{r, echo=FALSE}
var_imp <- compVarImp(all_models[["rf"]][["spec"]]@model[[1]], scale = FALSE)
# plotVarImp(var_imp)
plotVarImpHeatmap(var_imp, xlab = "Species", ylab = "Band")
```


# Trophic levels
```{r}
var_imp_levels = var_imp
for(i in seq(length(var_imp_levels))){
  var_imp_levels[[i]]$RESPONSE = tl$Level[grep(var_imp_levels[[i]]$RESPONSE[1], tl$Species)]
}
plotVarImpHeatmap(var_imp_levels, xlab = "Species", ylab = "Band")
```




When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
